Commutative Character Sheaves

### 2015-11-02 followup.tex
Reconstruction of Section 3.

\begin{abstract}
We introduce and establish the basic properties of  the category of \emph{commutative character sheaves} on smooth group schemes $G$ over finite fields $\Fq$. 
We use this category to geometrize types for supercuspidal representations of $p$-adic groups. 
\end{abstract}

@@

 \subsection{Statement of the main result}

As in [CS], every morphism of group schemes $G \to G'$ induces . .

Provisional hypothesis: suppose the smooth morphism $G\times G\to G\der$ is of relative dimension on each connected component of its image in $G\der$...\todo{This is another condition on $G$. Does it come from smoothness of $G$?}

\begin{theorem}\label{thm:Gab}
Under this hypothesis, pull-back along the abelianization $q : G \to G\ab$
\[
q^* : \CCS(G\ab) \to \CCS(G)
\]
is an equivalence of categories.
\end{theorem}

Theorem~\ref{thm:Gab} will be proved by factoring $\CCS(G\ab) \to \CCS(G\ab)$ according to the following diagram, which will be explained below, 
and by showing that each functor is an equivalence.
\[
\begin{tikzcd}
 \CCS(G)  &&& \arrow{lll}[swap]{q^*}  \CCS(G\ab) \arrow{d}{\text{Descent along torsor}} \\
\CCS_G(G)  \arrow{u}{\text{Equivariance}} &&& \arrow{lll}{\text{Change of Action}} \CCS_{G\der}(G) 
\end{tikzcd}
\]

\begin{remark}
Theorem~\ref{thm:Gab} provides an indication that $\CCS(G)$ is the correct category in which to geometrize characters of $G(\Fq)$. 
By contrast, $\CS(G)$ and $\CS(G\ab)$ are generally not isomorphic categories, not even when $G$ is a connected reductive algebraic group and $\Hh^1(\Fq,G\der)=0$, as we will see in Section~\ref{sec:stacky}.
\end{remark}

\subsection{Equivariance}

We wish to consider the categories $\CCS_G(G)$ (resp $\CS_G(G)$) of $G$-equivariant commutative character sheaves (linear character sheaves) on $G$. To that end, in this section we introduce that notion in its general context.

Let $G$ and $H$ be group schemes; let $a : H \times G\to G$ be a group action and write $p : H\times G \to G$ for projection. 
An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  $\nu : a^*\cs{L} \to p^*\cs{L}$ of Weil local systems on $G\times G$ such that the following diagram of local systems on $H\times H\times G$ commutes,
\[
\begin{tikzcd}
\ &  a_0^*  a^*\, \mathcal{L} \arrow{r}{a_0^*\nu} & a_0^* p^*\, \mathcal{L} & \\
a_1^* a^*\, \mathcal{L} \arrow{dr}[swap]{a_1^*\nu} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{p_2^*\nu} p_3^* a^*\, \mathcal{L} \\
& a_1^* p^*\, \mathcal{L} \arrow[equal]{r} & p_3^* p^*\, \mathcal{L}, & 
\end{tikzcd}
\]
where $a_0(x,y,z) = (x,a(y,z))$ and $a_1(x,y,z) = (a(x,y),z)$ and $p_3(x,y,z) = (y,z)$.
We remark that, on stalks, this condition is ...
\[
\begin{tikzcd}
\ &  \cs{L}_{x\cdot(y\cdot z)} \arrow{r}{\nu_{x,y\cdot z}} & \cs{L}_{y\cdot z} & \\
\cs{L}_{(x\cdot y)\cdot z} \arrow{dr}[swap]{\nu_{x\cdot y,z}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{y,z}} \cs{L}_{y\cdot z} \\
& \cs{L}_z \arrow[equal]{r} & \cs{L}_z & 
\end{tikzcd}
\]

Morphisms of $H$-equivariant Weil local systems are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which . . .

An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense that the following diagram of local systems on $H \times G\times G$ commutes ....
On stalks, this condition is
\[
\begin{tikzcd}
\ &  \cs{L}_{h\cdot (xy)} \arrow{r}{} & \cs{L}_{xy} & \\
\cs{L}_{(h\cdot x)(h\cdot y)} \arrow{dr}[swap]{} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{} \cs{L}_{xy} \\
& \cs{L}_{h\cdot x}\otimes \cs{L}_{h\cdot y} \arrow{r} & \cs{L}_x\otimes \cs{L}_y & 
\end{tikzcd}
\]

Write $\CS_H(G)$ for the category of $H$-equivariant linear character sheaves on $G$.
%\todo{Under construction}
%
Finally, an $H$-equivariant commutative character sheaf on $G$ is an $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ for whuch

\begin{lemma}
If $(\cs{L},\mu,\nu)$ is an equivariant linear character sheaf for the conjugation action of $G$ on $G$, then $(\cs{L},\mu)$ is a commutative character sheaf.
\end{lemma}

\begin{proof}
Let $a : G \times G \to G$ be the conjugation action $(g,h) \mapsto ghg^{-1}$ and let $p : G \times G \to G$ be projection to the second factor.
Let $\iota : G\to G$ be inversion for the group operation $m : G\times G\to G$.
Then $m = a \circ (p_1\times m\op)$ while $p \circ (p_1\times m\op) = m\op$.
Now, let $(\cs{L}, \mu, \nu)$ be an equivariant linear character sheaf.
Then
\begin{align*}
m^* \cs{L} 
&= (a \circ (p_1 \times m\op))^* \cs{L}\\
&= (p_1 \times m\op)^* a^* \cs{L}\\
&\iso (p_1 \times m\op)^* p^* \cs{L}\\
&= (p\circ (p_1 \times m\op))^* \cs{L}\\
&= m\op^* \cs{L}.
\end{align*}
The isomorphism above is
\[
\xi \ceq (p_1 \times m\op)^* \nu : m^* \cs{L}  \to m\op^* \cs{L}
\]
Observe that $p_1 \times m\op : G\times G \to G\times G$ is an isomorphism of varieties . . . 
The isomorphism $\xi$ satisfies the condition of Definition~\ref{def:CCS}. \todo{Checking this.}

Thus, $(\cs{L},\mu)$ is a commutative character sheaf.
\end{proof}

\begin{remark}
By Lemma~\ref{lem:symmetry}, the isomorphism $\xi_\nu$ is uniquely determined by $\mu$.
%This is the first hint that the forgetful functor may be an equivalence.
\end{remark}

\begin{lemma}\label{lem:equivariant}
The forgetful functor $\CCS_G(G)\to \CCS(G)$, given by $(\cs{L},\mu,\nu) \mapsto (\cs{L},\mu)$, is an equivalence.
\end{lemma}

\begin{proof}
Now, let $(\cs{L},\mu)$ be a commutative character sheaf.
Let $\xi: m^*\cs{L} \to m\op^*\cs{L}$ be an isomorphism satisfying the condition of Definition~\ref{def:CCS}.
Observe that $a = m \circ (m \times (\iota \circ p_1))$ while $m\op \circ (m \times (\iota \circ p_1)) = p$.
Then
\begin{align*}
a^* \cs{L} 
&= (m \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
&= (m \times (\iota \circ p_1))^* m^* \cs{L}\\
&\iso (m \times (\iota \circ p_1))^* m\op^* \cs{L}\\
&= (m\op \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
&= p^*\cs{L}.
\end{align*}
The isomorphism above is 
\[
\nu_\xi \ceq (m \times (\iota \circ p_1))^* \xi: a^*\cs{L} \to p^*\cs{L},
\]
 so $(\cs{L}, \mu, \nu_\xi)$ is a $G$-equivariant commutative character sheaf.

 forgetful  rule $(\cs{L},\mu)\to (\cs{L},\mu,\nu_\xi)$ and 
To define the promised adjunction, I need to modify the functors slighlty . . . 
\todo{This proof is under construction.}
\end{proof}

\begin{remark}
Lemma~\ref{lem:equivariant} shows that the `canonical functor' $\CCS(G) \to \CS(G)$ is a forgetful functor and also provides an alternate characterization of commutative character sheaves as linear (rank-$1$), multiplicative ($\mu$) and conjugation-equivariant ($\nu$) Weil local systems ($\phi$) on $\bG$. [Is this correct?]
\end{remark}

\subsection{Descent along torsors}

Let $G$ be a $k$-group scheme and let $H \to G$ be a closed subgroup scheme over $S$.

We now suppose that $H$ is normal in $G$ and that the fppf-quotient $G \to G'\ceq H\backslash G$ exists in group schemes over $\Fq$.
Then $q : G \to G'$ is a regular epimorphism with kernel pair $(n,p)$ in the category of schemes.
\[
\begin{tikzcd}
H\times G
 \arrow{r}[shift left]{n}
  \arrow{r}[shift right,swap]{p}
&
G 
\arrow{r}{q}
& 
G'
\end{tikzcd}
\]

Let $j : H \hookrightarrow G$ be the kernel of $q : G \to G'$ and let $m : G\times G \to G$ be multiplication for $G$. 
Write $n : H \times_S G \to G$ for the left action of $H$ on $G$; this is obtained by restricting the action $m : G\times G\to G$ to the subgroup $H\times G$. 
Let $n : H \times G \to G$ be the restriction of $m: G\times G \to G$.
Then $n = m \circ (j \times \id)$, so

 let $p : H\times_S G \to G$ be projection.

%In particular, $G \times_{G'} G \iso H\times_S G'$, so $G \to G'$ is a $G$-torsor in the fppf topology.
In this case we may factor the functor $\CCS(G') \to \CCS(G)$  . . . 
\[
\begin{tikzcd}
\CCS(G) &&\arrow{ll}[swap]{q^*} 
\CCS(G') \arrow{dl}{\text{`comparison'}}\\
& \arrow{ul}{\text{forget}} \CCS_{H}(G) & 
\end{tikzcd}
\]

\begin{lemma}\label{lem:descent}
The comparison functor $\CCS(G') \to \CCS_{H}(G)$ is an equivalence.
\end{lemma}

\begin{proof}
By descent theory, the functor $\Loc(G') \to \Loc_H(G)$ induced by $q: G \to G'$ is an equivalence of categories. Expand . . . 
\todo{Need to study the extra structure coming with character sheaves.}

%Let $j : C \hookrightarrow G$ be the kernel of $q : G \to G\ab$ and let $m : G\times G \to G$ be multiplication for $G$. 
Let $n : H \times G \to G$ be the restriction of $m: G\times G \to G$.
Then $n = m \circ (j \times \id)$, so
\begin{align*}
n^* \cs{L} 
&= (m \circ (j \times \id))^* \cs{L}\\
&= (j \times \id))^* m^*\cs{L}\\
&\iso (j \times \id))^* (\cs{L} \boxtimes \cs{L})\\
&= (j^*\cs{L}) \boxtimes \cs{L}\\
&= (\cs{L}\vert_C) \boxtimes \cs{L}\\
&= (\EE)_C \boxtimes \cs{L}\\
&= p^* \cs{L};
\end{align*}
the isomorphism above is 
\[
\nu_\mu \ceq(j \times \id))^* \mu: n^*\cs{L} \to p^*\cs{L}.
\]
Thus, every commutative character sheaf $\cs{L}$ on $G$ is $H$-equivariant.
It now follows from Lemma~\ref{lem:Lder} that the forgetful functor $\CCS_{G\der}(G) \to \CCS(G)$ is an equivalence. 
\end{proof}

@@

\[
\begin{tikzcd}
\arrow{dd}[swap]{f} G_1 \times G \arrow{dr}[swap]{a_1}{p} & \\
& G \\
G_2 \times G \arrow{ur}{a_2}[swap]{p} & 
\end{tikzcd}
\]

\begin{lemma}\label{lem:action}
The canonical functor
\[
\CS_{G_2}(G) \to \CS_{G_1}(G)
\]
is an equivalence if $f$ is dominant and  smooth of relative dimension on the connected components in its image.
\end{lemma}
\begin{proof}
\end{proof}

\subsection{Proof of the main result}

\begin{proof}[Proof of Theorem~\ref{thm:Gab}]
First we must see that $q^*$ factors according to . . . 
\[
\begin{tikzcd}
 \CCS(G)  &&& \arrow{lll}[swap]{q^*}  \CCS(G\ab) \arrow{d}{\text{Lem~\ref{lem:descent}}} \\
\CCS_G(G)  \arrow{u}{\text{Lem~\ref{lem:equivariant}}} &&& \arrow{lll}{\text{Lem~\ref{lem:action}}} \CCS_{G\der}(G) 
\end{tikzcd}
\]
\end{proof}

\begin{lemma}\label{lem:Lder}
If $\cs{L}\in \CCS(G)$ then $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
% Suppose Z(G) = 1$. If $\cs{L}\in \CS(G)$ and $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ then $\cs{L}\in \CCS(G)$. 
\end{lemma}

\begin{proof}
By construction, $c : G \times G \to G\der$ is dominant. 
Note that $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$. 
Pick $\cs{L}\in \CCS(G)$. 
Then
\begin{align*}
c^* (\cs{L}\vert_{G\der})
&=  (j\circ c)^*\cs{L} \\
&= (m\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
&= (m \times (\iota\circ m\op))^* m^* \cs{L} \\
&\iso (m \times (\iota\circ m\op))^* m\op^* \cs{L} \\
&= (m\op\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
&= e^* \cs{L}\\
&= (\EE)_{G\times G}.
\end{align*}
Since $c : G \times G \to G\der$ is schematically dense, $c^* (\cs{L}\vert_{G\der}) \iso (\EE)_{G\times G}$ implies $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ by Lemma~\ref{lem:dominant}. \todo{broken reference}

%Now, suppose $Z(G) =1$. Pick $\cs{L}\in \CS(G)$ and suppose $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
\end{proof}

>>>>

\begin{abstract}
We introduce and establish the basic properties of  the category of \emph{commutative character sheaves} on smooth group schemes $G$ over finite fields $\Fq$, building on earlier work by the same authors.
We use this category to geometrize types for supercuspidal representations of $p$-adic groups. 
\end{abstract}

@@

In this section we use descent along the abelianization $q : G \to G\ab$ to prove Propositions~1.2 and 1.4, and Theorem~\ref{thm:Gab}.

\subsection{Equivariant Weil local systems}

Let $G$ be as above.
Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
Let $a : H \times G\to G$ be a group action compatible with the group structure on $G$ and write $p : H\times G \to G$ for projection. 
Consider the morphisms
\[
\begin{tikzcd}
H \times H \times G 
\arrow[shift left=4]{r}{b_1} 
\arrow{r}{b_2} 
\arrow[shift right=4]{r}{b_3} 
& H \times G 
\arrow[shift left]{r}{a}
\arrow[shift right]{r}[swap]{p}
 & G 
\end{tikzcd}
\]
defined by $b_1(h_1,h_2,g) = (n(h_1,h_2),g)$,  $b_2(h_1,h_2,g) = (h_1,a(h_2,g))$ and $b_3(h_1,h_2,g) = (h_2,g)$.
Then, $a\circ b_1 = a\circ b_2$ and $a\circ b_3 = p\circ b_2$ and $p\circ b_1 = p\circ b_3$.
An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
\[
\nu : a^*\cs{L} \to p^*\cs{L}
\] 
of Weil local systems on $H\times G$ such that the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes,
\[
\begin{tikzcd}
\ &  \arrow{dl}[swap]{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}{p\circ b_2 = a\circ b_3} & \\
b_1^* a^*\, \mathcal{L} \arrow{dr}[swap]{b_1^*(\nu)} &&&&   \arrow{dl}{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L}, & 
\end{tikzcd}
\]
and $s^*(\nu) = \id_{\cs{L}}$.
In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations above; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
\iffalse
We remark that, on stalks, this condition is ...
\[
\begin{tikzcd}
\ &  \cs{L}_{x\cdot(y\cdot z)} \arrow{r}{\nu_{x,y\cdot z}} & \cs{L}_{y\cdot z} & \\
\cs{L}_{(x\cdot y)\cdot z} \arrow{dr}[swap]{\nu_{x\cdot y,z}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{y,z}} \cs{L}_{y\cdot z} \\
& \cs{L}_z \arrow[equal]{r} & \cs{L}_z & 
\end{tikzcd}
\]
\fi
%
Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
\[
\begin{tikzcd}
\arrow{d}[swap]{\nu} a^*\cs{L} \arrow{r}{a^*(\alpha)} & a^*\cs{L}' \arrow{d}{\nu'} \\
p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
\end{tikzcd}
\]
commutes.
This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.

\subsection{Equivariant linear character sheaves}

An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense. 
Consider the morphisms $c_1 : H \times G\times G \to G\times G$, $c_2 : H \times G\times G \to H\times G$ and $c_3 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),a(h,g_2))$ and $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$ and $c_3(h, g_1, g_2) = (g_1, g_2)$. 
Then $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ if $(\cs{L},\mu)$ is a linear character sheaf on $G$ and the following diagram of Weil local systems on $H \times G\times G$ commutes.
\[
\begin{tikzcd}
\arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} & \arrow{l}[swap]{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{r}{p\circ c_2 = m\circ c_3}  & c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{r} & (p^*\cs{L}) \boxtimes (p^*\cs{L}) & \arrow{l}[swap]{\nu\boxtimes \nu}  (a^*\cs{L}) \boxtimes (a^*\cs{L}) & \arrow{l} c_3^*(\cs{L}\boxtimes \cs{L})
\end{tikzcd}
\]
In this diagram, the arrows not labeled are derived from canonical isomorphisms.
\iffalse
On stalks, this condition is
\[
\begin{tikzcd}
\ &  \cs{L}_{h\cdot (xy)} \arrow{r}{} & \cs{L}_{xy} & \\
\cs{L}_{(h\cdot x)(h\cdot y)} \arrow{dr}[swap]{} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{} \cs{L}_{xy} \\
& \cs{L}_{h\cdot x}\otimes \cs{L}_{h\cdot y} \arrow{r} & \cs{L}_x\otimes \cs{L}_y & 
\end{tikzcd}
\]
\fi
%
A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves, so
\[
\begin{tikzcd}
\arrow{d}{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
\end{tikzcd}
\]
commutes.
%
Let $\CS_H(G)$ be the category of $H$-equivariant linear character sheaves on $G$.

Is $\CS_H(G)$ a rigid monoidal category?

\subsection{Descent along a torsor}

Now suppose $q : G \to G'$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
\[
\begin{tikzcd}
H\times G
 \arrow[shift left]{r}{a}
  \arrow[shift right,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
G'
\end{tikzcd}
\]
Let $\cs{L}'$ be a linear character sheaf on $G'$.
Consider the functor
\[
q^* : \CS(G') \to \CS(G)
\]
given on objects by $(\cs{L}',\mu') \mapsto (q^*\cs{L}', (q\times q)^* \mu', \nu_{\cs{L}'})$; cf [Dictionary].
Then $q^*\cs{L}'$ is an $H$-equivariant linear character sheaf on $G$ when equipped with the canonical isomorphism
\[
\nu_{\cs{L}'} : a^* q^* \cs{L}' \mathop{\longrightarrow}\limits^{\iso} (q\circ a)^* \cs{L}' = (q\circ p)^*\cs{L}' \mathop{\longrightarrow}\limits^{\iso} p^* q^*\cs{L}.
\]
This simple observation shows that the functor $q^* : \CS(G') \to \CS(G)$  factors according to the following commuting diagram of functors
\[
\begin{tikzcd}
\CS(G) &&\arrow{ll}[swap]{q^*} 
\CS(G') \arrow{dl}{\text{`comparison'}}\\
& \arrow{ul}{\text{forget}} \CS_{H}(G). & 
\end{tikzcd}
\]

\begin{lemma}
If $q : G \to G'$ is an $H$-torsor in the fppf topology then the comparison functor $\CS(G') \to \CS_H(G)$ is an equivalence.
\end{lemma}

\begin{proof}
. . . 
So the lemma reduces to the claim: the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence. 
To see this, observe first that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
Moreover, if $Y \to X$ is a flat surjective morphism of affine schemes over $\Fq$, then the comparison functor $\Loc(X) \to \Loc(Y\to X)$ is an equivalence, with $\Loc(Y\to X)$ defined as in [].
It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fppf topology.
(This is a small variation on the proof of the fact that quasicoherent sheaves form a stack on sheaves in the fppf topology.)
Since $q : G\to G'$ is an $H$-torsor in the fppf topology, is now follows immediately that the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence.
\end{proof}

\subsection{Forget}

In this section we find a subcategory $\CS'(G)$ of $\CS(G)$ such that the forgetful functor $\CS_H(G) \to \CS(G)$ induces an equivalence $\CS_H(G) \to \CS'(G)$, in the case required to prove Proposition~1.2.

Suppose there is some $H\times G\to G\times G$ such that the following diagram commutes.
\[
\begin{tikzcd}
&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
G & & G \\
& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p} & 
\end{tikzcd}
\]
Then $f_1 : H\times G \to G$ and $f_0 : H \to G$ . . .

\begin{lemma}
If $f: H\times G \to G$ exists as above and $f_1$ is proper, then the forgetful functor $\CS_H(G) \to \CS(G)$ is full and faithful, with essential image
$\CS'(G)$ consisting of those $(\cs{L},\mu,\nu) \in \CS_H(G)$ such that $f_0^*\cs{L} \iso (\EE)_{H}$. 
\end{lemma}

\begin{proof}
\end{proof}

\subsection{Proof of Proposition~1.2}

We now consider a special case of the lemmas above. 
Suppose $H = G$ and the action $a$ is $m: G\times G\to G$.
Suppose $H' = G\der$ and let $a'$, be the restriction of $m$ to $G\der\times G$.
Let $d : G\der \hookrightarrow G$ and set $k(h,g) = d(h)$. 
Then $f : G\der \times G\to G\times G$ is simply the inclusion.

As we have seen above, the fppf quotient $q : G\to G\ab = G/G\der$ exists in schemes and is a $G\der$-torsor in the fppf topology. 
%(In fact, it's a trivial torsor in that topology.)
It follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
On the other hand, by Lemma~[], the forgetful functor $\CS_{G\der}(G)\to \CS(G)$ defines an equivalence $\CS_{G\der}(G)\to \CS'(G)$, where $\CS'(G)$ is the category of $(\cs{L},\mu,\nu)\in \CS_{G\der}(G)$ such that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
It now follows that $q^* : \CS(G\ab) \to \CS(G)$ is fll and faithful with essential image $\CS'(G)$.
This concludes the proof of Proposition~1.2.

\subsection{Commutative character sheaves}

Move this statement to Section 1?

\begin{theorem}\label{thm:Gab}
Pull-back along the abelianization $q : G \to G\ab$
\[
q^* : \CCS(G\ab) \to \CCS(G)
\]
is an equivalence of categories.
\end{theorem}

\begin{proof}
Combining Lemmas~[] and [] we see that $q^* : \CS(G\ab) \to \CS(G)$ is full and faithful.
% with essential image $\CS'(G)$, the category of linear character sheaves $\cs{L}$ on $G$ for which $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$. 
By Definition~[], this induces an equivalence between $\CCS(G\ab)$ and $\CCS(G)$. 
\end{proof}

\subsection{Proof of Proposition~1.4}

\iffalse

@@

Now, let $a' : H'\times G \to G$ be another group action on $G$ and suppose $f: H \times G \to H'\times G$ makes the following diagram commute.
\[
\begin{tikzcd}
&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
G & & G \\
& \arrow{ul}{a'} H' \times G \arrow{ur}[swap]{p} & 
\end{tikzcd}
\]
Then pull-back along $f: H\times G \to H'\times G$ defines a monoidal functor 
\[
\CS_{H'}(G) \to \CS_{H}(G).
\]

Then $f : H\times G \to H'\times G$ is given by $f(h,g) = (k(h,g),g)$ for some $k : H\times G\to H'$. 
Define $d : H\to H'$ by $d(h) = k(h,1)$.

\begin{lemma}\label{lem:action}
The canonical functor
\[
\CS_{H}(G) \to \CS_{H'}(G)
\]
is an equivalence if ...
\end{lemma}
\begin{proof}
\end{proof}

\subsection{Conjugation}

We close this section with an alternate characterization of $\CS'(G)$, the category of linear character sheaves $\cs{L}$ on $G$ for which $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
Recall that $\CS'(G)$ is a full subcategory of $\CS(G)$ and that $\CCS(G)$ is a full subcategory of $\CS'(G)$.

Consider the following case of Section~\ref{ssec:action}.

\fi
